Synpotic Soil Characterization

### 2022-12-21 3-reports/characterization_report.Rmd
plot ions
overall summaries in report

@@

```{r, icr-vk}
tar_read(gg_icr_vankrevelen)
```

```{r, icr-unique}
tar_read(gg_icr_unique)
```

```{r, icr-pca}
tar_read(gg_icr_pca)
```

>>>>

## OVERALL SUMMARIES

```{r analyte-completion}
tar_read(analysis_completion_matrix) %>% knitr::kable()
```

```{r overall-pca}
tar_read(gg_pca_all)
```

```{r correlations-all}
tar_read(gg_correlations)
```

@@

```{r, icr-vk, fig.height=16, fig.width=16}
tar_read(gg_icr_vankrevelen)
```

```{r, icr-unique, fig.height=16, fig.width=16}
tar_read(gg_icr_unique)
```

```{r, icr-pca, fig.height=5, fig.width=5}
tar_read(gg_icr_pca)$biplot_all
```

```{r, icr-pca-regions, fig.height=5, fig.width=10}
tar_read(gg_icr_pca)$biplot_regions
```

```{r, ions, fig.height=16, fig.width=16}
tar_read(gg_ions)
```
